---
title: "Simulation"
author: "Bohdan Horak"
date: "Saturday, August 23, 2014"
output: pdf_document
---
## Summary
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.  


Illustrate via simulation and associated explanatory text the properties of the
distribution of the mean of 40 exponential(0.2)s.  You should
## Question 1

### 1.Show where the distribution is centered at and compare it to the theoretical center of the distribution.

```{r,fig.height=3,fig.width=4}
nosim <- 10000
n <- 40
set.seed(1)
means<-apply(matrix( rexp(nosim * n, rate=0.2), nosim), 1, mean)
mean_val<-mean(means)
sds<-sd(means)
theo_sd<-5/sqrt(40)
hist(means,breaks=50,col="magenta")

```

From the resuling simulation the distribution has a mean `r mean_val` which is very
close to the theoretical mean of 1/lambda=1/0.2=5.

### 2. Show how variable it is and compare it to the theoretical variance of the distribution.

The statndard deviation of the simulation is `r sds` which is also close to the 
theoretical standard deviation of SD=s/sqrt(n)=5/sqrt(40)=`r theo_sd`.

### 3. Show that the distribution is approximately normal.

```{r,fig.height=3,fig.width=4,echo=F}
# Add a Normal Curve (Thanks to Peter Dalgaard)
x <- means
h<-hist(x, breaks=50, col="red", xlab="Miles Per Gallon", 
      main="Histogram with Normal Curve") 
xfit<-seq(min(x),max(x),length=40) 
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x)) 
yfit <- yfit*diff(h$mids[1:2])*length(x) 
lines(xfit, yfit, col="blue", lwd=2)
```

This is the same histogram as before but overlayed with a normal curve. Clearly
is approximatly normal, even with a small bin size. This is a very good example
of the central limit theorem which confirms that the distribution of the sample means
is approximetly normal as the sample size gets larger.

### 4. Evaluate the coverage of the confidence interval for 1/lambda
```{r}
nosim<-10000
count<-0
for (i in 1:nosim) {
    temp<-rexp(n,rate=0.2)
    x_bar<-mean(temp)
    sd_bar<-sd(temp)
    ci_l<-x_bar-1.96*sd_bar/sqrt(40)
    ci_u<-x_bar+1.96*sd_bar/sqrt(40)
    if (ci_l<5 & 5<ci_u) {
      count<-count+1  
    } 
}
coverage<-100*count/nosim
```

Simulated coverage for a sample size of `r n` for the confidence interval is about 
`r coverage` %.Note that the intervals provided in the assignment are biased downwards, 
that's why the coverage is relatively low.

For the more complete .rmd code please visit my [Github repo](https://github.com/bhorak/Stat_Inference)

