---
title: "ToothGrowth"
author: "Bohdan Horak"
date: "Saturday, August 23, 2014"
output: pdf_document
fontsize: 10pt
---

## Exploratory

```{r,echo=FALSE,include=FALSE}
library(ggplot2);library(gridExtra);
data(ToothGrowth)
```

Here is a summary of the data.

```{r,echo=FALSE}
summary(ToothGrowth)
```

Here are a couple bar plots demonstrating the differences between the two supplements,
by dosage.

```{r,echo=FALSE,fig.height=2.5}
df<-ToothGrowth
x<-aggregate(len~supp+dose,mean,data=df)
dose_05<-x[x$dose==0.5,]
dose_1<-x[x$dose==1,]
dose_2<-x[x$dose==2,]


barplot1 <- qplot(x=supp, y=len, fill=supp,data=dose_05, geom="bar",stat="identity",position="dodge")+ggtitle("0.5 Dosage")+ guides(fill=FALSE)
barplot2 <- qplot(x=supp, y=len, fill=supp,data=dose_1, geom="bar",stat="identity",position="dodge")+ggtitle("1.0 Dosage")+ guides(fill=FALSE)
barplot3 <- qplot(x=supp, y=len, fill=supp,data=dose_2, geom="bar",stat="identity",position="dodge")+ggtitle("2.0 Dosage")+ guides(fill=FALSE)
grid.arrange(barplot1,barplot2,barplot3,ncol=3)
```

As we can see "OJ" either outperforms or equals the "VC" supplement.We can't say so 
conclusively so we do some inference.

## Inference

For this data set I will perform a hypothesis test on wether the means of the 
"OJ" and "VC" are equal. We assume a significane level=5%, that is if the "p"
value from our tests is less than 5% we can reject the null hypothesis that 
there is no difference between the means.Note we assume equal variance in each test.

```{r,echo=FALSE}
data_0.5<-df[df$dose==0.5,]
data_1<-df[df$dose==1,]
data_2<-df[df$dose==2,]
```

### 0.5 Dosage

```{r}
t.test(len~supp, paired=F,var.equal=F,data=data_0.5)
```
As the resultin p value is less than 5% we can say that OJ is statistically better
at encouraging tooth growth than VC is.

### 1.0 Dosage

```{r}
t.test(len~supp, paired=F,var.equal=F,data=data_1)
```


As the resultin p value is less than 5% we can say that OJ is statistically better
at encouraging tooth growth than VC is.

### 2.0 Dosage

```{r}
t.test(len~supp, paired=F,var.equal=F,data=data_2)
```

As the resultin p value is greater than 5% we can say that OJ is not statistically different
at encouraging tooth growth than VC is.

